---
title: "Pictures of mODa14"
output:
  html_document:
    self_contained: false
---

```{r setup, include=FALSE}

all_files <- sort(list.files("pictures"))

pics <- all_files[
  grepl("\\.(jpg|jpeg|png|webp|gif)$",
        all_files,
        ignore.case = TRUE)
]

videos <- all_files[
  grepl("\\.(mp4|mov|webm)$",
        all_files,
        ignore.case = TRUE)
]

```

<style>
html {
  visibility: hidden;
}
</style>

<div class="slideshow-container">

<a class="prev" onclick="plusSlides(-1)">❮</a>
<a class="next" onclick="plusSlides(1)">❯</a>

```{r slides, echo=FALSE, results='asis'}

for (p in pics) {

  cat(
    paste0(
      '<img class="slide" src="pictures/',
      p,
      '" loading="lazy">\n'
    )
  )

}

for (v in videos) {

  cat(
    paste0(
      '<video class="slide" controls preload="metadata">',
      '<source src="pictures/',
      v,
      '" type="video/mp4">',
      '</video>\n'
    )
  )

}

```

</div>

<script>

let slideIndex = 1;

document.addEventListener("DOMContentLoaded", function() {

  showSlides(slideIndex);

  document.documentElement.style.visibility = "visible";
});

function plusSlides(n) {
  showSlides(slideIndex += n);
}

function showSlides(n) {

  let slides = document.getElementsByClassName("slide");

  if (slides.length === 0) return;

  if (n > slides.length) {
    slideIndex = 1;
  }

  if (n < 1) {
    slideIndex = slides.length;
  }

  for (let i = 0; i < slides.length; i++) {
    slides[i].style.display = "none";
  }

  slides[slideIndex - 1].style.display = "block";
}

document.addEventListener("keydown", function(event) {

  if (event.key === "ArrowRight") {
    plusSlides(1);
  }

  if (event.key === "ArrowLeft") {
    plusSlides(-1);
  }

});

</script>

<style>

body {
  max-width: 100%;
  margin: auto;
}

.slideshow-container {
  position: relative;
  max-width: 95vw;
  margin: auto;
}

.slide {
  display: none;
  width: 100%;
  max-height: 85vh;
  object-fit: contain;
  background-color: black;
}

video.slide {
  width: 100%;
  max-height: 85vh;
}

.prev,
.next {
  cursor: pointer;
  position: absolute;
  top: 50%;
  padding: 16px;
  color: white;
  font-size: 28px;
  font-weight: bold;
  border-radius: 50%;
  background: rgba(0,0,0,0.5);
  transform: translateY(-50%);
  user-select: none;
}

.prev {
  left: 15px;
}

.next {
  right: 15px;
}

.prev:hover,
.next:hover {
  background: rgba(0,0,0,0.8);
}

</style>